Concurrent Programming with CXL

### 2020-06-05 book/paper.tex
Fixed error reporting.  Said something about TLA+ and constants in book

@@

>>>>

CXL is heavily influenced by TLA+, TLC, and PlusCal~\cite{}.
CXL is designed to have a lower learning curve than those
systems, but is not as powerful.  When you finish this book
and want to learn more, we strongly encourage checking
those out.

@@

In CXL, constants have a default, but those can be overridden on the command
line using the \texttt{-c} option.
For example, if you want to test the code for \texttt{N = 100}, run:
\begin{code}
\begin{verbatim}
$ cxl -c N=100 triangle.cxl
#states = 103
no issues found
$
\end{verbatim}
\end{code}
